Revisiting the Relationship between Short-Chain Fatty Acids, the Microbiota, and Colorectal Tumors

### 2018-08-07 submission/manuscript.Rmd
paragraph 1 discussion Ada suggestions

The observations from this study do not support the hypothesis that SCFA concentrations are different in individuals with tumors. Whether we directly measured the SCFA concentration or investigated genes associated with their production, no difference could be identified between individuals without tumors and patients with adenomas or carcinomas [Figure 1 & 2]. Although there were differences in the number of significant correlations between SCFA concentration and OTU relative abundance based on whether individuals did not have tumors, had an adenoma, or had a carcinoma, SCFA concentrations did not provide increased model accuracy for tumor classification [Figure 3-4 & S1]. Instead, SCFA concentrations provided similar information to what specific OTUs were already providing to the tumor classification models [Figure 4]. Additionally, when models using OTU relative abundance to classify SCFA concentrations were assessed, the OTUs that classified to *Clostridiales*, *Lachnospiraceae*, and *Ruminococcaceae* were not the same as the OTUs that classified to  these taxa in the tumor models [Figure 4-5]. Collectively, our observations suggest that resident taxa from *Clostridiales*, *Lachnospiraceae*, and *Ruminococcaceae*, that are different between individuals without tumors and patients with adenomas or carcinomas, are not that same as those involved with SCFA production.

>>>>

The observations from this study do not support the hypothesis that SCFA concentrations are different in individuals with tumors. Whether we directly measured the SCFA concentration or investigated genes that encoded enzymes used for their production, no difference could be identified between individuals without tumors and patients with adenomas or carcinomas [Figure 1 & 2]. Although there were differences in the number of significant correlations between SCFA concentration and OTU relative abundance based on whether individuals did not have tumors, had an adenoma, or had a carcinoma, SCFA concentrations did not provide increased model accuracy for tumor classification [Figure 3-4 & S1]. In models with SCFA concentrations included, many OTUs that classified to *Clostridiales*, *Lachnospiraceae*, and *Ruminococcaceae* remained as important variables for the model [Figure 4]. Additionally, when models using OTU relative abundance to classify SCFA concentrations were assessed, the OTUs that classified to *Clostridiales*, *Lachnospiraceae*, and *Ruminococcaceae* were not the same as the OTUs that classified to these taxa in the tumor models [Figure 4-5]. Collectively, our observations suggest that the resident taxa from *Clostridiales*, *Lachnospiraceae*, and *Ruminococcaceae* that are different between individuals without tumors and patients with adenomas or carcinomas, are not the same as those involved with SCFA production.

### 2018-08-07 submission/manuscript.tex
paragraph 1 discussion Ada suggestions

The observations from this study do not support the hypothesis that SCFA
concentrations are different in individuals with tumors. Whether we
directly measured the SCFA concentration or investigated genes
associated with their production, no difference could be identified
between individuals without tumors and patients with adenomas or
carcinomas {[}Figure 1 \& 2{]}. Although there were differences in the
number of significant correlations between SCFA concentration and OTU
relative abundance based on whether individuals did not have tumors, had
an adenoma, or had a carcinoma, SCFA concentrations did not provide
increased model accuracy for tumor classification {[}Figure 3-4 \&
S1{]}. Instead, SCFA concentrations provided similar information to what
specific OTUs were already providing to the tumor classification models
{[}Figure 4{]}. Additionally, when models using OTU relative abundance
to classify SCFA concentrations were assessed, the OTUs that classified
to \emph{Clostridiales}, \emph{Lachnospiraceae}, and
\emph{Ruminococcaceae} were not the same as the OTUs that classified to
these taxa in the tumor models {[}Figure 4-5{]}. Collectively, our
observations suggest that resident taxa from \emph{Clostridiales},
\emph{Lachnospiraceae}, and \emph{Ruminococcaceae}, that are different
between individuals without tumors and patients with adenomas or
carcinomas, are not that same as those involved with SCFA production.

>>>>

The observations from this study do not support the hypothesis that SCFA
concentrations are different in individuals with tumors. Whether we
directly measured the SCFA concentration or investigated genes that
encoded enzymes used for their production, no difference could be
identified between individuals without tumors and patients with adenomas
or carcinomas {[}Figure 1 \& 2{]}. Although there were differences in
the number of significant correlations between SCFA concentration and
OTU relative abundance based on whether individuals did not have tumors,
had an adenoma, or had a carcinoma, SCFA concentrations did not provide
increased model accuracy for tumor classification {[}Figure 3-4 \&
S1{]}. In models with SCFA concentrations included, many OTUs that
classified to \emph{Clostridiales}, \emph{Lachnospiraceae}, and
\emph{Ruminococcaceae} remained as important variables for the model
{[}Figure 4{]}. Additionally, when models using OTU relative abundance
to classify SCFA concentrations were assessed, the OTUs that classified
to \emph{Clostridiales}, \emph{Lachnospiraceae}, and
\emph{Ruminococcaceae} were not the same as the OTUs that classified to
these taxa in the tumor models {[}Figure 4-5{]}. Collectively, our
observations suggest that the resident taxa from \emph{Clostridiales},
\emph{Lachnospiraceae}, and \emph{Ruminococcaceae} that are different
between individuals without tumors and patients with adenomas or
carcinomas, are not the same as those involved with SCFA production.
